---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bayesefa

<!-- badges: start -->
[![R-CMD-check](https://github.com/tmsalab/bayesefa/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/bayesefa/actions)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![CRAN Version Badge](http://www.r-pkg.org/badges/version/bayesefa)](https://cran.r-project.org/package=bayesefa)
[![CRAN Status](https://cranchecks.info/badges/worst/bayesefa)](https://cran.r-project.org/web/checks/check_results_bayesefa.html)
[![RStudio CRAN Mirror's Monthly Downloads](http://cranlogs.r-pkg.org/badges/bayesefa?color=brightgreen)](http://www.r-pkg.org/pkg/bayesefa)
[![RStudio CRAN Mirror's Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/bayesefa?color=brightgreen)](http://www.r-pkg.org/pkg/bayesefa)
<!-- badges: end -->

Exploratory Bayesian factor analysis of continuous, mixed-type, and bounded continuous variables using the mode-jumping algorithm of Man and Culpepper (2020).

## Installation

You can install `bayesefa` from CRAN using:

```{r cran-installation, eval = FALSE}
install.packages("bayesefa")
```

Or, you can be on the cutting-edge development version on GitHub using:

```{r gh-installation, eval = FALSE}
if(!requireNamespace("remotes")) install.packages("remotes")
devtools::install_github("tmsalab/bayesefa")
```

## Usage

To use the `bayesefa` package, load it into _R_ using:

```{r example, message = FALSE}
library("bayesefa")
```

## Authors

Albert Man and Steven Andrew Culpepper

## Citing the `bayesefa` package

To ensure future development of the package, please cite `bayesefa`
package if used during an analysis or simulation studies. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("bayesefa")
```

## License

GPL-3
